Untitled

### 2025-02-24 script/nighttime_adm2.Rmd
import folders

```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"
```

```{r}
night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

print(night_wgs84)

```{r}
shapefile_path <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_0.shp"

country <- readOGR(shapefile_path)

if (!identical(crs(night_wgs84), crs(country))) {
  country <- spTransform(country, crs(night_wgs84))
}

# Recadrer et masquer le raster night_wgs84_recode selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country))
night_wgs84_masked <- mask(night_wgs84_cropped, country)

rm(shapefile_path, night_wgs84_cropped)

dev.off()

plot(night_wgs84_masked)
```

```{r}
library(exactextractr)
library(scales)

regions <- st_read("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_BEN_2.shp")
regions <- st_make_valid(regions)

png("plots/ntl/test2.png", width = 800, height = 600)

ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold")) +
  labs(title = "Benin - NTL ADM2 - Round 7")

dev.off()

#NTL Maps
##2016
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2016.tif"

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

###ADM2

```{r}

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ","MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==7)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 7", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r7.jpg"), plot = plot, width = 10, height = 8)

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

###ADM2
```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==6)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 6", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r6.jpg"), plot = plot, width = 10, height = 8)

##2011
```{r}
tiff_file <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/nighttime_recode/Harmonized_DN_NTL_2011.tif"

night <- raster(tiff_file)

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

###ADM2

```{r}
data_trust_report_adm2_valid <- readRDS("Data/Data_RDS/data_trust_report_adm2_valid.rds")

countries_adm2 <- c("BEN", "BFA","BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER","SEN", "SLE", "TGO")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

panel_sf <- data_trust_report_adm2_valid %>%
  filter(ISO == country, round==5)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

labels = label_number(accuracy = 0.01)

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM2 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)

###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

output_dir <- "C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/maps/ntl/"

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

# Recadrer et masquer le raster night_wgs84 selon les frontières du country
night_wgs84_cropped <- crop(night_wgs84, extent(country_shp))
night_wgs84_masked <- mask(night_wgs84_cropped, country_shp)

panel_sf <- data_trust_report_adm1_valid %>%
  filter(ISO == country, round==5)

panel_sf <- st_as_sf(panel_sf, coords = c("longitude", "latitude"), crs = st_crs(regions))

plot <- ggplot() +
  geom_sf(data = regions, aes(fill = mean_night_log), color = "white") +
  scale_fill_distiller(palette = "YlOrBr", direction = 1, name = "log(DN)", breaks = c(min(regions$mean_night_log), max(regions$mean_night_log)), labels = c(0,5)) +
    geom_point(data = panel_sf, aes(x = caplong, y = caplat), color = "black", size = 4, shape=17) +
  theme_minimal() +
  theme(legend.position = "right", plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),axis.title.x = element_blank(),           axis.title.y = element_blank()) +
  labs(title = paste(country, "- NTL ADM1 - Round 5", sep = " "))

  ggsave(filename = paste0(output_dir, country, "_NTL_map_r5.jpg"), plot = plot, width = 10, height = 8)

}
```

@@

print(night)

night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

@@

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

@@

data_trust_test%<>%
  select(-c("mean_night", "mean_night_log"))

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust_test)

data_trust_test%>%
  select(mean_night, ISO, round)%>%
  filter(!is.na(mean_night))%>%
  View()

```
###ADM1
```{r}
countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=8)

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)
```

@@

###ADM2
```{r}

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

@@

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=7)

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

@@

###ADM2
```{r}
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO")

@@

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=6)

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

@@

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust_test)

```
###ADM1
```{r}

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

for (country in countries_adm1) {

  # Lecture du fichier shapefile
  shapefile <- paste0("C:/Users/Redha CHABA/Documents/Working paper/Trust/Script/data/data_Raw/gadm41_", country,"_1.shp")
  regions <- st_read(shapefile)
  regions <- st_make_valid(regions)

regions %<>%
  rename(ISO=GID_0)%>%
  select(ISO, NAME_1, mean_night, mean_night_log)%>%
  mutate(round=5)

data_trust_test %<>% left_join(accumulated_results, by=c("ISO", "NAME_1", "round"))

data_trust_test %<>%
  mutate(mean_night = coalesce(mean_night.x, mean_night.y))%>%
  mutate(mean_night_log = coalesce(mean_night.x, mean_night.y))%>%
  select(-c(mean_night_log.x, mean_night_log.y, mean_night.x, mean_night.y))

data_trust_test%<>%
  distinct(id_unique, .keep_all = TRUE)

@@

```{r}
saveRDS(data_trust_test, file="Data/Data_RDS/data_trust_test_report2.rds")

write_dta(data_trust_test, "Data/Data_dta/data_trust_test_report2.dta")

>>>>

@@

#print(night)

#night_wgs84 <- projectRaster(night, crs = CRS("+proj=longlat +datum=WGS84"))

@@

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO","GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

@@

accumulated_results%<>%
  rename(mean_night_2=mean_night,
         mean_night_log_2=mean_night_log)

glimpse(accumulated_results)

data_trust <- readRDS("Data/Data_RDS/final_df5.rds")

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

glimpse(data_trust)
```

@@

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

@@

accumulated_results%<>%
  rename(mean_night_2=mean_night,
         mean_night_log_2=mean_night_log)

glimpse(accumulated_results)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

data_trust %<>%
  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))

glimpse(data_trust)

@@

countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE", "SEN", "TGO", "GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")

@@

accumulated_results%<>%
  rename(mean_night_2=mean_night,
         mean_night_log_2=mean_night_log)

glimpse(accumulated_results)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

data_trust %<>%
  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))

glimpse(data_trust)
```

@@

accumulated_results%<>%
  rename(mean_night_2=mean_night,
         mean_night_log_2=mean_night_log)

glimpse(accumulated_results)

data_trust %<>% left_join(accumulated_results, by=c("ISO", "NAME_2", "round"))

data_trust%<>%
  distinct(id_unique, .keep_all = TRUE)

data_trust %<>%
  mutate(mean_night_2 = coalesce(mean_night_2.x, mean_night_2.y))%>%
  mutate(mean_night_log_2 = coalesce(mean_night_log_2.x, mean_night_log_2.y))%>%
  select(-c(mean_night_log_2.x, mean_night_log_2.y, mean_night_2.x, mean_night_2.y))

glimpse(data_trust)

@@

```{r}
saveRDS(data_trust, file="Data/Data_RDS/final_df5.rds")
write_dta(data_trust, "Data/Data_dta/final_df5.dta")
```
